Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects

### 2024-01-09 paper.tex
Number of triangles

\subsection{Execution times for our algorithms}
In this section we measure execution times of our algorithms for random
3-dimensional arrays of bits (i.e. each element can be either 0 or 1). The
arrays have equal number of elements along each direction therefore
representing cubes of 2-phase porous media. The number of voxels in each cube
increases from $1.25 \cdot 10^5$ to $2.7 \cdot 10^7$ linearly. The time of execution
is measured for each function executed on a CPU and a GPU. Hardware and software
components used for testing are listed in \cref{tab:machine}.
\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|}
    CPU & Intel Celeron 333 MHz \\
    RAM & 100500 GB DDR4 PC-XXXX \\
    GPU & AMD Navi 21 \\
    Julia & 1.10.0 \\
    CUDA.jl & 4.0
  \end{tabular}
  \caption{Parameters of the machine used to measure execution times of the
    algorithms described in this paper.}
  \label{tab:machine}
\end{table*}
\begin{figure*}[tp]
  \centering
  \subfigure[CPU]{
    \includegraphics[width=0.4\linewidth]{images/timings-cpu.png}}
  \hfill
  \subfigure[GPU]{
    \includegraphics[width=0.4\linewidth]{images/timings-gpu.png}}
  \caption[]{Execution times of the algorithms proposed in this paper.}
  \label{fig:timings}
\end{figure*}
The results are on \cref{fig:timings}. It can be observed that the time of
execution is a power function of number of voxels. GPU gives a
10x-100x performance boost depending on the correlation function.

>>>>

\subsection{Execution times for our algorithms}
In this section we measure execution times of our algorithms for random
3-dimensional arrays of bits (i.e. each element can be either 0 or 1). The
arrays have equal number of elements along each direction therefore
representing cubes of 2-phase porous media. The number of voxels $N$ in each
cube increases from $1.25 \cdot 10^5$ to $2.7 \cdot 10^7$ linearly. Times of
execution are measured for each function executed on a CPU and a GPU. Hardware
and software components used for testing are listed in \cref{tab:machine}. Each
computation of a correlation function is equivalent to testing $N^{5/3}$ pattern
triangles thrown into the sample.
\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|}
    CPU & Intel Celeron 333 MHz \\
    RAM & 100500 GB DDR4 PC-XXXX \\
    GPU & AMD Navi 21 \\
    Julia & 1.10.0 \\
    CUDA.jl & 4.0
  \end{tabular}
  \caption{Parameters of the machine used to measure execution times of the
    algorithms described in this paper.}
  \label{tab:machine}
\end{table*}
\begin{figure*}[tp]
  \centering
  \subfigure[CPU]{
    \includegraphics[width=0.4\linewidth]{images/timings-cpu.png}}
  \hfill
  \subfigure[GPU]{
    \includegraphics[width=0.4\linewidth]{images/timings-gpu.png}}
  \caption[]{Execution times of the algorithms proposed in this paper.}
  \label{fig:timings}
\end{figure*}
The results are on \cref{fig:timings}. It can be observed that the time of
execution is a power function of number of voxels. GPU gives a
10x-100x performance boost depending on the correlation function.
